\documentclass{article}
\begin{document}
\noindent
Andreas Landgrebe
\\
Laboratory Assignment \# 1 : Introducing Data Management Concepts and Tools
\\
\textbf{3. A complete description of the features that data management tolls should provide}
\\
\\
When it comes data management tools, there are several features that should one should be provided. A data management tool is a tool to best handle ones data. When thinking of such tools, there are three word that come up to mind. The first word is Simplified. By definition of these tools, ones data should not have gotten more complicated. The next word that comes up to mind to define what a data management tool is would be optimized. When loading all of these data, one does not want such data to become as accessible as before. The last word that comes up to is integrated. When setting up a tool like this, there should be many formats that it is being to access. Some of the several features that comes up to mind would be being able to do backup data. If anything should happen to any of these data, one would want to make sure that there is a back-up for this data so nothing terrible happens to ones data. Another feature that one looks for is to be able to store the data into the database. The whole purpose of the data management tool is to manage ones data and if one is not able to use such a tool to be able to store data into a database, when the database would not be doing its purpose correctly. The next feature is to modify the data. When all of these data is in a database and would like to change any of the data in it, a data management tool should be able to modify data. Another feature that one would want in a data management tool is to insert data. When one adds data to a database, one might also want to put more data into the database to store and a data management tool should be able to do that. The next feature that is important for a data management tool to have is to delete data. If there is data in a database that one does not want anymore, then one should be able to delete this specific data from the database using this tool. Another feature that is important for the tool is to be able query data. To be able to query data is to be able to request information from a database. To be able to request information from a database is important in order to make data accessible and this tool has to be able to do so. The next feature would be able to support concurrence. When concurrence is supports in a data management tool, then it ensures that the correct results are being generated as quickly as possible.
The last feature that one would for in a data management tool would be support many formats. It is important for a data management tool to be able to select different formats for different personal preferences. This tool is important in order to customize different pieces of data. In my experience, the most important feature for a data management tool would be to simplify data. To be able to simplify data would mean that the database would be more user friendly for a piece of software to be user friendly is key to me.
\end{document}